---
title: "The code for: Role of urban vegetation in air phytoremediation: Differences between scientific research and environmental management perspectives"
author: "Cheng gong"
date: "2023/3/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = TRUE, 
                      error = FALSE)
```

# Load packages
```{r load_packages}
library(brms)
library(tidyverse)
library(ggridges)
library(tidybayes)
library(glue)
library(zCompositions)
library(ggpubr)
```

# Data preparing

```{r load_data_from_files}
# load the data for meta-analysis
es_mergednox <- read_csv("./data/es_nox_pooled.csv")
es_mergedo3 <- read_csv("./data/es_o3_pooled.csv")
es_mergedpm <- read_csv("./data/es_pm_pooled.csv")
es_mergedso2 <- read_csv("./data/es_so2_pooled.csv")
es_mergedgas <- read_csv("./data/es_g_pooled.csv")
es_mergedsolid <- read_csv("./data/es_s_pooled.csv")
es_merged <- read_csv("./data/es_allexp_pooled.csv")
es_regdata <- readRDS("./data/es_regdata.RData")
es_regdiv <- readRDS("./data/es_regdiv.RData")
# color data for forest plot
color_forest <- readRDS("./data/color_forest.RData")
```

# Figure 1: Effect size of pollutants reduction

## set the prior information for models

```{r set_prior_of_model}
 priors_nox <- c(prior(normal(-0.3,0.5), class = Intercept),
              prior(cauchy(0,0.5), class = sd))
 priors_pm <- priors_nox
 priors_so2 <- priors_nox
 priors_gas <- priors_nox
 priors_solid <- priors_nox
 priors_o3 <- c(prior(normal(0.1, 0.5), class = Intercept),
                prior(cauchy(0, 0.5), class = sd))
```

## build bayesian random-effect model

```{r build_model_random_intercept}
# Pooled effect for PM
bay_pm <- brm(es_adj|se(se_adj) ~ 1 + (1|caselab),
              data = es_mergedpm,
              family = "gaussian",
              prior = priors_pm, 
              iter = 5000,
              seed = 123,
              control = list(adapt_delta = 0.99),
              cores = 8)

# Pooled effect for SO2
bay_so2 <- brm(es_adj|se(se_adj) ~ 1 + (1|caselab),
               data = es_mergedso2,
               family = "gaussian",
               prior = priors_so2, 
               iter = 5000,
               seed = 123,
               control = list(adapt_delta = 0.99),
               cores = 8)

# Pooled effect for O3
bay_o3 <- brm(es_adj|se(se_adj) ~ 1 + (1|caselab),
              data = es_mergedo3,
              family = "gaussian",
              prior = priors_o3, 
              iter = 5000,
              seed = 123,
              control = list(adapt_delta = 0.99),
              cores = 8)

# Pooled effect for NOx
bay_nox <- brm(es_adj|se(se_adj) ~ 1 + (1|caselab), 
               data = es_mergednox,
               family = "gaussian",
               prior = priors_nox,
               iter = 10000,
               seed = 123, 
               control = list(adapt_delta = 0.995),
               cores = 8)
# save bayesian models to files 			   
saveRDS(bay_nox, file = "./model/bay_nox.RData")
saveRDS(bay_o3, file = "./model/bay_o3.RData")
saveRDS(bay_so2, file = "./model/bay_so2.RData")
saveRDS(bay_pm, file = "./model/bay_pm.RData")
```

## Draw the forest plot for reduction effect

```{r prepare_data_for_drawing}
# load model for drawing
bay_nox <- readRDS(file = "./model/bay_nox.RData")
bay_o3 <- readRDS(file = "./model/bay_o3.RData")
bay_so2 <- readRDS(file = "./model/bay_so2.RData")
bay_pm <- readRDS(file = "./model/bay_pm.RData")
bm_nox <- bay_nox$fit
bm_o3 <- bay_o3$fit
bm_so2 <- bay_so2$fit
bm_pm <- bay_pm$fit

# A simple function to extract numbers of observations in the bayesian model
numoflevesl <- function(brmsfit){
  dim(ranef(brmsfit)[[1]])[1]
}

numobs_case <- c(numoflevesl(bay_nox),numoflevesl(bay_o3),
                 numoflevesl(bay_so2),numoflevesl(bay_pm))

# extract posterior samples for fixed effect				 
posterior_noxp <- bm_nox %>%
        spread_draws(b_Intercept) %>%
        mutate(caselab = "NOx",
               fillc = color_forest$nox_fill)
posterior_o3p <- bm_o3 %>%
        spread_draws(b_Intercept) %>%
        mutate(caselab = "O3",
               fillc = color_forest$o3_fill)
posterior_so2p <- bm_so2 %>%
        spread_draws(b_Intercept) %>%
        mutate(caselab = "SO2",
               fillc = color_forest$so2_fill)
posterior_pmp <- bm_pm %>%
        spread_draws(b_Intercept) %>%
        mutate(caselab = "PM",
               fillc = color_forest$pm_fill)
# bind all effect together
posterior_allp <- bind_rows(posterior_noxp, posterior_o3p,
                            posterior_so2p, posterior_pmp)
posterior_allp <- posterior_allp %>%
        mutate(caselab = factor(caselab, levels = c("NOx", "O3", "SO2", "PM")))

posterior_allp_summ <- posterior_allp %>%
        group_by(caselab) %>%
        mean_qi(b_Intercept, .width = 0.95) %>%
        rename(lower95 = .lower, upper95 = .upper) %>%
        mutate(mean_l = sprintf("%0.2f", b_Intercept),
        l95 = sprintf("%0.2f", lower95),
        u95 = sprintf("%0.2f", upper95)) %>%
        mutate(n.obs = as.character(numobs_case))

lkup <- data.frame(p_type1 = c("NOX", "O3", "SO2", "PM"),
                   p_type1f = c("NOx", "O3", "SO2", "PM"),
                   stringsAsFactors = FALSE)
true_obs_all <- es_merged %>% 
        dplyr::select(caselab, p_type1, es_adj, var_adj) %>%
        left_join(lkup, by = "p_type1") %>% 
        mutate(p_type1f = factor(p_type1f, levels =c("NOx", "O3", "SO2", "PM"))) %>%
        rename(b_Intercept = es_adj, clab = caselab, caselab = p_type1f)
```

```{r draw_the_plot}
theme_forest2 <- theme(axis.title = element_text(size = 25, colour = "black"), 
                      axis.text.x = element_text(size = 20, colour = "black"),
                      axis.text.y = element_text(size = 20, colour = "black"),
                      panel.background = element_rect(fill = "white", colour = "black"),
                      panel.grid = element_blank(),
                      legend.position = "none",
                      plot.margin = unit(rep(1,4), "cm"))

fig_forest_allp <- posterior_allp %>% 
        ggplot(aes(x = b_Intercept, y = caselab, fill = caselab)) +   
        stat_halfeye(.width = 0.95, size = 2, point_interval = mean_qi, scale = 0.5) + 
        geom_boxplot(data = true_obs_all, aes(x = b_Intercept, y = caselab, fill = caselab),
                     width = 0.05, position = position_nudge(y = -0.06),outlier.alpha = 0) + 
        geom_vline(xintercept = 0, linetype = 2, size = 1.2, color = "red") + 
        scale_fill_manual(values = as.character(unlist(color_forest)[1:4])) +
        scale_y_discrete(labels = c(expression(NO[x]), expression(O[3]),
                                    expression(SO[2]), expression(PM))) + 
        geom_text(data = posterior_allp_summ, 
                  aes(x = 0.3,
                      label = glue("{n.obs},    {mean_l},    [{l95}, {u95}]")),
                  hjust = "outward", size = 6,
                  position = position_nudge(y = 0.2)) + 
        annotate(geom = "text", x = 0.3, y = 4.5, 
                 label = "n,    mean,    95%CrI",
                 hjust = "outward", size = 6) + 
        xlim(-1.5, 1.5) + 
        labs(y = "",
             x = "Effect size (LRR) of pollutants reduction") + 
        theme_forest2

ggsave("./fig/fig1.eps", plot = fig_forest_allp,
       width = 250, height = 200, units = "mm", limitsize = FALSE,
       scale = 1)        
```


# Figure 2: Sub-group analysis: distribution pattern, seasons, types of greenspaces

## Define the function for sub-meta analysis
```{r define_submeta}
# A function to automatically build model formula
paste_formual <- function(popef, grpef, intercept = TRUE){
  left <- "es_adj|se(se_adj) ~ "
  random <- paste("(", "1", "|", grpef, ")")
  if(!intercept){
    popef <- paste(popef, "-1", sep = "")
  }
  fma <- paste(left, popef, "+", random, sep = "")
  return(fma)
}

# A function for running the sub-meta analysis
# data: the data.frame object
# popef: population effect (fixed effect)
# grpef : group effect (random effect), outer group should be the first element, then inner group
# brmspara: the parameters for running the brms model (MC sampling parameters included)
# nested: should the random factors be nested in the model
# onlynested: only fited the nested model
# intercept: Compared with intercept?
# This function has a large memory overhead and is more stable on systems with more than 16gb of memory
sub_single <- function(data, popef, grpef, brmspara, nested = FALSE, onlynested = FALSE, 
                       intercept = TRUE){
  if (nested){
    nested_grp <- paste(grpef[1], grpef[2], sep = "/")
    grpef <- c(grpef, nested_grp)
  }
  mod_formula <- t(outer(popef, grpef, FUN = paste_formual, intercept = intercept))
  mod_names <- t(outer(popef, grpef, FUN = paste, sep = "_"))
  mod_formula <- as.character(mod_formula)
  mod_names <- as.character(mod_names)
  if(!onlynested){
    print(paste("We have", length(mod_formula), "models.", sep = " "))
    brms_list <- vector(mode = "list", length = length(mod_formula))
    for(i in seq_along(mod_formula)){
      print(paste("Fitting model:", mod_formula[i], sep = " "))
      mod_i <- brm(formula = formula(mod_formula[i]), data = data,
                   cores = brmspara$cores, seed = brmspara$seed, iter = brmspara$iter,
                   control = list(max_treedepth = brmspara$max_treedepth,
                                  adapt_delta = brmspara$adapt_delta))
      brms_list[[i]] <- mod_i
    }
    names(brms_list) <- mod_names
  }else{
    # nested random term
    print(paste("We have", length(mod_formula[3]), "models.", sep = " "))
    brms_list <- vector(mode = "list", length = length(mod_formula[3]))
    print(paste("Fitting model:", mod_formula[3], sep = " "))
    mod_i <- brm(formula = formula(mod_formula[3]), data = data,
                  cores = brmspara$cores, seed = brmspara$seed, iter = brmspara$iter,
                  control = list(max_treedepth = brmspara$max_treedepth,
                                adapt_delta = brmspara$adapt_delta))
    brms_list[[1]] <- mod_i
    names(brms_list) <- mod_names[3]
  }
  return(brms_list)
}
```

## build sub meta bayesian model

### NOx sub-meta

#### subpoint vs sepoint
```{r submeta_nox_point_dis}
df_nox <- es_regdata %>% filter(p_type1 == "NOX")
popef <- c("point_dis")
grpef <- c("caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 12, adapt_delta = 0.99)

submeta_nox <- sub_single(data = df_nox, popef = popef, grpef = grpef, 
                          nested = FALSE, brmspara = brmspara, intercept = FALSE)
saveRDS(submeta_nox, "./model/submeta_nox_pointdis.RData")
```

#### leaf vs fallen (seasons of the year)

```{r submeta_nox_seasons}
popef <- c("leaf")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 12, adapt_delta = 0.99)

submeta_nox <- sub_single(data = df_nox, popef = popef, grpef = grpef, 
                          nested = FALSE, brmspara = brmspara, intercept = FALSE)
saveRDS(submeta_nox, "./model/submeta_nox_leaf.RData")
```

#### landtype_exp

```{r submeta_nox2}
df_nox <- rename(df_nox, gi = landtype_exp)
popef <- c("gi")
grpef <- c("stulab", "caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 12, adapt_delta = 0.99)

submeta_nox <- sub_single(data = df_nox, popef = popef, grpef = grpef, 
                          nested = TRUE, onlynested = TRUE, brmspara = brmspara, 
                          intercept = FALSE)
saveRDS(submeta_nox, "./model/submeta_nox_gi.RData")
```

### O3 sub-meta

#### subpoint vs sepoint
```{r submeta_o3}
df_o3 <- es_regdata %>% filter(p_type1 == "O3")
popef <- c("point_dis")
grpef <- c("caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 11, adapt_delta = 0.99)

submeta_o3 <- sub_single(data = df_o3, popef = popef, grpef = grpef, 
                          nested = FALSE, brmspara = brmspara, intercept = FALSE)
saveRDS(submeta_o3, "./model/submeta_o3_pointdis.RData")
```

#### leaf vs fallen (seasons of the year)

```{r submeta_nox2}
popef <- c("leaf")
grpef <- c("stulab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 11, adapt_delta = 0.99)

submeta_o3 <- sub_single(data = df_o3, popef = popef, grpef = grpef, 
                          nested = FALSE, brmspara = brmspara, intercept = FALSE)
saveRDS(submeta_o3, "./model/submeta_o3_leaf.RData")
```


#### landtype_exp

```{r submeta_nox2}
df_o3 <- rename(df_o3, gi = landtype_exp)
popef <- c("gi")
grpef <- c("caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 11, adapt_delta = 0.99)

submeta_o3 <- sub_single(data = df_o3, popef = popef, grpef = grpef, 
                          nested = FALSE, brmspara = brmspara, intercept = FALSE)
saveRDS(submeta_o3, "./model/submeta_o3_gi.RData")
```

### PM sub-meta

#### subpoint vs sepoint
```{r submeta_PM}
df_pm <- es_regdata %>% filter(p_type1 == "PM")
popef <- c("point_dis")
grpef <- c("caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 11, adapt_delta = 0.99)

submeta_pm <- sub_single(data = df_pm, popef = popef, grpef = grpef, 
                          nested = FALSE, brmspara = brmspara, intercept = FALSE)
saveRDS(submeta_pm, "./model/submeta_pm_pointdis.RData")
```

#### leaf vs fallen (seasons of the year)

```{r submeta_pm}
popef <- c("leaf")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 11, adapt_delta = 0.99)

submeta_pm <- sub_single(data = df_pm, popef = popef, grpef = grpef, 
                          nested = FALSE, brmspara = brmspara, intercept = FALSE)
saveRDS(submeta_pm, "./model/submeta_pm_leaf.RData")
```


#### landtype_exp

```{r submeta_pm}
df_pm <- rename(df_pm, gi = landtype_exp)
popef <- c("gi")
grpef <- c("stulab", "caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 11, adapt_delta = 0.99)

submeta_pm <- sub_single(data = df_pm, popef = popef, grpef = grpef, 
                          nested = TRUE, onlynested = TRUE, brmspara = brmspara, 
                         intercept = FALSE)
saveRDS(submeta_pm, "./model/submeta_pm_gi.RData")
```

### SO2 sub-meta

#### subpoint vs sepoint
```{r submeta_SO2}
df_so2 <- es_regdata %>% filter(p_type1 == "SO2")
popef <- c("point_dis")
grpef <- c("caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 11, adapt_delta = 0.99)

submeta_so2 <- sub_single(data = df_so2, popef = popef, grpef = grpef, 
                          nested = FALSE,brmspara = brmspara, 
                          intercept = FALSE)
saveRDS(submeta_so2, "./model/submeta_so2_pointdis.RData")
```

#### leaf vs fallen

```{r submeta_pm}
popef <- c("leaf")
grpef <- c("stulab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 5000,
                 max_treedepth = 11, adapt_delta = 0.99)

submeta_so2 <- sub_single(data = df_so2, popef = popef, grpef = grpef, 
                          nested = FALSE, brmspara = brmspara, intercept = FALSE)
saveRDS(submeta_so2, "./model/submeta_so2_leaf.RData")
```


#### landtype_exp

```{r submeta_pm}
df_so2 <- rename(df_so2, gi = landtype_exp)
popef <- c("gi")
grpef <- c("stulab", "caselab")
# only 1 observations in park group, remove it.
df_so2 <- filter(df_so2, gi != "Park")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 4000,
                 max_treedepth = 13, adapt_delta = 0.99)

submeta_so2 <- sub_single(data = df_so2_or, popef = popef, grpef = grpef, 
                          nested = TRUE, onlynested = TRUE, brmspara = brmspara, 
                          intercept = FALSE)
saveRDS(submeta_so2, "./model/submeta_so2_gi.RData")
```

## draw the results of sub-meta

### load models

```{r load_submeta_model}
# nox
sub_nox_pointdis <- readRDS("./model/submeta_nox_pointdis.RData")
sub_nox_leaf <- readRDS("./model/submeta_nox_leaf.RData")
sub_nox_gi <- readRDS("./model/submeta_nox_gi.RData")
# o3
sub_o3_pointdis <- readRDS("./model/submeta_o3_pointdis.RData")
sub_o3_leaf <- readRDS("./model/submeta_o3_leaf.RData")
sub_o3_gi <- readRDS("./model/submeta_o3_gi.RData")
# so2
sub_so2_pointdis <- readRDS("./model/submeta_so2_pointdis.RData")
sub_so2_leaf <- readRDS("./model/submeta_so2_leaf.RData")
sub_so2_gi <- readRDS("./model/submeta_so2_gi.RData")
# pm
sub_pm_pointdis <- readRDS("./model/submeta_pm_pointdis.RData")
sub_pm_leaf <- readRDS("./model/submeta_pm_leaf.RData")
sub_pm_gi <- readRDS("./model/submeta_pm_gi.RData")
```

### function for drawing
```{r build_function_to_draw_submeta}
# This function draw information from the a brmsfit object, and applied a simple test of hypothesis
info_submeta <- function(brmsfit, usehyp = TRUE){
  r2 <- bayes_R2(brmsfit)
  fef <- fixef(brmsfit)
  hypl <- combn(rownames(fef), 2)
  hypl <- apply(hypl, 2, paste, collapse = "<")
  if (usehyp){
    hyp_res <- lapply(hypl, 
                      FUN = function(x){hypothesis(brmsfit, x)})
  }else{
    hyp_res <- NULL
  }
  
  return(list(r2 = r2, fixef = fef, hyp = hyp_res))
}

# This function draw posterior samples from a brmsfit object and return a summary of posterior samples.
extract_submeta <- function(brmsfit, trtname, pname){
  post_samples <- posterior_samples(brmsfit, "^b")
  df_o <- brmsfit$data
  mod_name <- colnames(df_o)[3]
  colnames(df_o)[3] <- "mods"
  n_obs <- df_o %>% count(mods)
  n_obs$trtname <- trtname
  n_obs <- n_obs %>% arrange(trtname)
  colnames(post_samples) <- trtname
  post_samples <- post_samples %>% 
    pivot_longer(cols = all_of(trtname), 
    values_to = "value", names_to = "types") %>%
    mutate(mods = mod_name, 
           pollutants = pname)
  post_summ <- post_samples %>%
    group_by(types) %>%
    mean_qi(value, width = c(0.95)) %>%
    rename(lower95 = value.lower, upper95 = value.upper) %>%
    mutate(mods = mod_name) %>%
    mutate(nobs = n_obs$n, pollutants = pname)
    return(list(samples = post_samples,
                summarise = post_summ))
}
```

### point distribution

```{r draw_submeta_pointdis}
trtname <- c("Separate Points", "Sub-points")
nl <- c("NOx", "O3", "SO2", "PM")
point_nox <- extract_submeta(sub_nox_pointdis$point_dis_caselab, trtname, "NOx")
point_o3 <- extract_submeta(sub_o3_pointdis$point_dis_caselab, trtname, "O3")
point_so2 <- extract_submeta(sub_so2_pointdis$point_dis_caselab, trtname, "SO2")
point_pm <- extract_submeta(sub_pm_pointdis$point_dis_caselab, trtname, "PM")

post_pointdis <- bind_rows(point_nox$samples, point_o3$samples, point_so2$samples, point_pm$samples)
pointdis_summ <- bind_rows(point_nox$summarise, point_o3$summarise, point_so2$summarise, 
                           point_pm$summarise)
post_pointdis <- post_pointdis %>%
  mutate(pollutants = factor(pollutants, levels = nl))
pointdis_summ <- pointdis_summ %>%
  mutate(pollutants = factor(pollutants, levels = nl))
pointdis_summ <- pointdis_summ %>% 
  mutate(l95 = sprintf("%0.2f", lower95),
         u95 = sprintf("%0.2f", upper95),
         val = sprintf("%0.2f", value))
ant_lb <- "n,   mean,   95%CrI"

submeta_theme <- theme(panel.grid = element_blank(), 
                       panel.background = element_rect(fill = "white", color = "black"),
                       axis.title = element_text(size = 20), 
                       axis.text.x = element_text(size = 18), 
                       axis.text.y = element_text(size = 18), 
                       legend.position = "bottom", 
                       legend.text = element_text(size = 15))
y_axlb <- c("NOx" = expression(NO[x]), 
            "O3" = expression(O[3]),
            "SO2" = expression(SO[2]),
            "PM" = expression(PM))

fig_subpoint <- ggplot(data = post_pointdis, aes(x = value, y = pollutants, fill = types)) + 
  geom_text(data = pointdis_summ, aes(label = glue("n={nobs}, {val}, [{l95}, {u95}]"), x = 0.5), hjust = "outward", vjust = 3.5, position = position_dodge(1), size = 6) + 
  stat_halfeye(.width = 0.95, size = 2, 
               position = position_dodge(1), 
               point_interval = mean_qi, scale = 1) + 
  geom_vline(xintercept = 0, linetype = "dashed", size = 1, color = "steelblue") + 
  geom_hline(yintercept = c(1.35, 2.36, 3.35), linetype = "twodash", color = "grey", size = 1) + 
  annotate(geom = "text", x = 0.5, y = 4.4, label = ant_lb, size = 6, hjust = "outward") + 
  scale_x_continuous(limits = c(-1.5, 2.2)) + 
  labs(x = "Effect size (LnRR)", y = "") + 
  guides(fill = guide_legend(title = NULL)) + 
  scale_fill_manual(values = c("#00BFFF", "#FF3030")) + 
  scale_y_discrete(labels = y_axlb) + 
  submeta_theme

ggsave(filename = "./fig/fig_subpoint.eps", plot = fig_subpoint,
       width = 170, height =250 , units = "mm", limitsize = FALSE)
saveRDS(fig_subpoint, "./fig/fig_subpoint.RData")
```

```{r test_of_hypothesis_for_point_dis}
# caculate the probability for p(separate - subpoint)
dishyp_nox <- info_submeta(sub_nox_pointdis$point_dis_caselab)$hyp
dishyp_o3 <- info_submeta(sub_o3_pointdis$point_dis_caselab)$hyp
dishyp_so2 <- info_submeta(sub_so2_pointdis$point_dis_caselab)$hyp
dishyp_pm <- info_submeta(sub_pm_pointdis$point_dis_caselab)$hyp
```

### leaf fallen
```{r draw_leaf_submeta}
trtname <- c("Defoliation", "Leaf")
nl <- c("NOx", "O3", "SO2", "PM")
leaf_nox <- extract_submeta(sub_nox_leaf$leaf_caselab, trtname, "NOx")
leaf_o3 <- extract_submeta(sub_o3_leaf$leaf_stulab, trtname, "O3")
leaf_so2 <- extract_submeta(sub_so2_leaf$leaf_stulab, trtname, "SO2")
leaf_pm <- extract_submeta(sub_pm_leaf$leaf_caselab, trtname, "PM")

post_samples <- bind_rows(leaf_nox$samples, leaf_o3$samples, leaf_so2$samples, leaf_pm$samples)
post_summ <- bind_rows(leaf_nox$summarise, leaf_o3$summarise, leaf_so2$summarise, 
                           leaf_pm$summarise)

post_samples <- post_samples %>%
  mutate(pollutants = factor(pollutants, levels = nl))
post_summ <- post_summ %>%
  mutate(pollutants = factor(pollutants, levels = nl))
post_summ <- post_summ %>% 
  mutate(l95 = sprintf("%0.2f", lower95),
         u95 = sprintf("%0.2f", upper95),
         val = sprintf("%0.2f", value))
ant_lb <- "n,   mean,   95%CrI"

fig_leaffall <- ggplot(data = post_samples, aes(x = value, y = pollutants, fill = types)) + 
  geom_text(data = post_summ, aes(label = glue("n={nobs}, {val}, [{l95}, {u95}]"), x = 0.5), hjust = "outward", vjust = 3, position = position_dodge(1), size = 6) + 
  stat_halfeye(.width = 0.95, size = 2, 
               position = position_dodge(1), 
               point_interval = mean_qi, scale = 1) + 
  geom_vline(xintercept = 0, linetype = "dashed", size = 1, color = "steelblue") + 
  geom_hline(yintercept = c(1.35, 2.36, 3.35), linetype = "twodash", color = "grey", size = 1) + 
  annotate(geom = "text", x = 0.5, y = 4.4, label = ant_lb, size = 6, hjust = "outward") + 
  scale_x_continuous(limits = c(-1.5, 2.2)) + 
  labs(x = "Effect size (LnRR)", y = "") + 
  guides(fill = guide_legend(title = NULL)) + 
  scale_fill_manual(values = c("#FFC125", "#2E8B57")) + 
  scale_y_discrete(labels = y_axlb) + 
  submeta_theme

ggsave(filename = "./fig/fig_leaffall.eps", plot = fig_leaffall,
       width = 170, height = 250, units = "mm", limitsize = FALSE)
saveRDS(fig_leaffall, "./fig/fig_leaffall.RData")
```

```{r test_of_hypothesis_for_season}
# caculate the probability for p(winter - summer) (p(leaf fallen season - leaf growing season))
seahyp_nox <- info_submeta(sub_nox_leaf$leaf_caselab)$hyp
seahyp_o3 <- info_submeta(sub_o3_leaf$leaf_stulab)$hyp
seahyp_so2 <- info_submeta(sub_so2_leaf$leaf_stulab)$hyp
seahyp_pm <- info_submeta(sub_pm_leaf$leaf_caselab)$hyp
```

### green land type

```{r draw_submeta_greentype}
trtname <- c("Forest", "Roadside tree", "Park", "Small patch")
land_nox <- extract_submeta(sub_nox_gi$`gi_stulab/caselab`, trtname, "NOx")
land_o3 <- extract_submeta(sub_o3_gi$gi_caselab, trtname, "O3")
land_so2 <- extract_submeta(sub_so2_gi$`gi_stulab/caselab`, trtname[c(1, 2, 4)], "SO2")
land_pm <- extract_submeta(sub_pm_gi$`gi_stulab/caselab`, trtname, "PM")

post_samples <- bind_rows(land_nox$samples, land_o3$samples, land_so2$samples, land_pm$samples)
post_summ <- bind_rows(land_nox$summarise, land_o3$summarise, land_so2$summarise, 
                           land_pm$summarise)
post_samples <- post_samples %>%
  mutate(pollutants = factor(pollutants, levels = nl))
post_summ <- post_summ %>%
  mutate(pollutants = factor(pollutants, levels = nl))
post_summ <- post_summ %>% 
  mutate(l95 = sprintf("%0.2f", lower95),
         u95 = sprintf("%0.2f", upper95),
         val = sprintf("%0.2f", value))
ant_lb <- "n,   mean,   95%CrI"

fig_landexp <- ggplot(data = post_samples, aes(x = value, y = pollutants, fill = types)) + 
  geom_text(data = post_summ, aes(label = glue("n={nobs}, {val}, [{l95}, {u95}]"), x = 0.9), hjust = "outward", vjust = 2, position = position_dodge(0.7), size = 6) + 
  stat_halfeye(.width = 0.95, size = 2, 
               position = position_dodge(0.7), 
               point_interval = mean_qi, scale = 0.7) + 
  geom_vline(xintercept = 0, linetype = "dashed", size = 1, color = "steelblue") + 
  geom_hline(yintercept = c(1.35, 2.36, 3.35), linetype = "twodash", color = "grey", size = 1) + 
  annotate(geom = "text", x = 0.9, y = 4.4, label = ant_lb, size = 6, hjust = "outward") + 
  labs(x = "Effect size (LnRR)", y = "") + 
  guides(fill = guide_legend(title = NULL)) + 
  scale_y_discrete(labels = y_axlb) + 
  scale_fill_manual(values = c("#00CD00", "#00B2EE", "#FFA500", "#FF4500"))+
  submeta_theme

saveRDS(fig_landexp, file = "./fig/fig_landexp.RData")
ggsave(filename = "./fig/fig_landexp.eps", plot = fig_landexp,
       width = 170, height = 250, units = "mm", limitsize = FALSE)
```

```{r test_of_hypothesis_for_land_type}
# caculate the probability for 6 combination of hypothesis 
gihyp_nox <- info_submeta(sub_nox_gi$`gi_stulab/caselab`)$hyp
gihyp_o3 <- info_submeta(sub_o3_gi$gi_caselab)$hyp
gihyp_so2 <- info_submeta(sub_so2_gi$`gi_stulab/caselab`)$hyp
gihyp_pm <- info_submeta(sub_pm_gi$`gi_stulab/caselab`)$hyp
```

### Combine figures in a grid figure

```{r submeta_allinone}
fig_subpoint <- readRDS("./fig/fig_subpoint.RData")
fig_leaffall <- readRDS("./fig/fig_leaffall.RData")
fig_landexp <- readRDS("./fig/fig_landexp.RData")

fig_submeta <- ggarrange(fig_subpoint, fig_leaffall, fig_landexp, nrow = 1,
                         ncol = 3, labels = letters[c(1:3)],
                         font.label = list(size = 25, face = "bold"))
ggsave(filename = "./fig/fig2.eps", plot = fig_submeta,
       width = 510, height = 250, units = "mm", limitsize = FALSE)
saveRDS(fig_submeta, file = "./fig/fig2.RData")
```

# Figure 3: Sub-group analysis: leaf types and life forms

## Prepare data
```{r prepare_data_for_fig3}
es_regdivlite <- es_regdiv %>% 
  dplyr::select(author, year, area, Journal, method, p_type1, stulab, stuid, caselab, 
         obid_l1, es_adj, var_adj, se_adj, `dominant species`, family, 
         leaf_type, evergreen_forest, habitus) %>%
  mutate(reduction = ifelse(es_adj > 0, "None", "Reduction"))
es_regdivpm <- es_regdivlite %>% filter(p_type1 == "PM")
es_regdivnox <- es_regdivlite %>% filter(p_type1 == "NOX")
es_regdivo3 <- es_regdivlite %>% filter(p_type1 == "O3")
es_regdivso2 <- es_regdivlite %>% filter(p_type1 == "SO2")
```

## build models

### leaf type and life forms analysis for PM

```{r pm_leaftype_life_forms}
# leaf shape 
popef <- c("leaf_type")
grpef <- c("stulab", "caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 3000,
                 max_treedepth = 12, adapt_delta = 0.99)

sub_pm_leaftrait <- sub_single(data = es_regdivpm %>% filter(leaf_type != "None"),
                               popef = popef, grpef = grpef, nested = TRUE, brmspara = brmspara,
                               intercept = FALSE)
saveRDS(sub_pm_leaftrait, file = "./model/sub_pm_leaftrait.RData")

# forest_type
popef <- c("evergreen_forest")
sub_pm_foresttype <- sub_single(data = es_regdivpm %>% filter(evergreen_forest != "None"),
                               popef = popef, grpef = grpef, nested = TRUE, brmspara = brmspara,
                               intercept = FALSE)
saveRDS(sub_pm_foresttype, file = "./model/sub_pm_foresttype.RData")
```

### leaf type and life forms analysis for NOx

```{r nox_leaftype_life_forms}
# leaf shape 
popef <- c("leaf_type")
grpef <- c("stulab", "caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 3000,
                 max_treedepth = 12, adapt_delta = 0.99)

sub_nox_leaftrait <- sub_single(data = es_regdivnox %>% filter(leaf_type != "None"),
                               popef = popef, grpef = grpef, nested = TRUE, brmspara = brmspara,
                               intercept = FALSE)
saveRDS(sub_nox_leaftrait, file = "./model/sub_nox_leaftrait.RData")

# forest_type
popef <- c("evergreen_forest")
sub_nox_foresttype <- sub_single(data = es_regdivnox %>% filter(evergreen_forest != "None"),
                               popef = popef, grpef = grpef, nested = TRUE, brmspara = brmspara,
                               intercept = FALSE)
saveRDS(sub_nox_foresttype, file = "./model/sub_nox_foresttype.RData")
```

### leaf type and life forms analysis for O3

```{r o3_leaftype_life_forms}
# o3
# leaf shape 
popef <- c("leaf_type")
grpef <- c("stulab", "caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 3000,
                 max_treedepth = 12, adapt_delta = 0.99)

sub_o3_leaftrait <- sub_single(data = es_regdivo3 %>% filter(leaf_type != "None"),
                               popef = popef, grpef = grpef, nested = TRUE, brmspara = brmspara,
                               intercept = FALSE)
saveRDS(sub_o3_leaftrait, file = "./model/sub_o3_leaftrait.RData")

# forest_type
popef <- c("evergreen_forest")
sub_o3_foresttype <- sub_single(data = es_regdivo3 %>% filter(evergreen_forest != "None"),
                               popef = popef, grpef = grpef, nested = TRUE, brmspara = brmspara,
                               intercept = FALSE)
saveRDS(sub_o3_foresttype, file = "./model/sub_o3_foresttype.RData")
```

### leaf type and life forms analysis for SO2

```{r so2_leaftype_life_forms}
#SO2
# leaf shape 
popef <- c("leaf_type")
grpef <- c("stulab", "caselab")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 3000,
                 max_treedepth = 12, adapt_delta = 0.99)

sub_so2_leaftrait <- sub_single(data = es_regdivso2 %>% filter(leaf_type != "None"),
                               popef = popef, grpef = grpef, nested = TRUE, brmspara = brmspara,
                               intercept = FALSE)
saveRDS(sub_so2_leaftrait, file = "./model/sub_so2_leaftrait.RData")

# forest_type
popef <- c("evergreen_forest")
sub_so2_foresttype <- sub_single(data = es_regdivso2 %>% filter(evergreen_forest != "None"),
                               popef = popef, grpef = grpef, nested = TRUE, brmspara = brmspara,
                               intercept = FALSE)
saveRDS(sub_so2_foresttype, file = "./model/sub_so2_foresttype.RData")
```

## draw the results of submeta

### load models
```{r read_leaf_trait_models}
# read model from files
# PM
sub_pm_foresttype <- readRDS("./model/sub_pm_foresttype.RData")
sub_pm_leaftrait <- readRDS("./model/sub_pm_leaftrait.RData")
# SO2
sub_so2_foresttype <- readRDS("./model/sub_so2_foresttype.RData")
sub_so2_leaftrait <- readRDS("./model/sub_so2_leaftrait.RData")
# O3
sub_o3_foresttype <- readRDS("./model/sub_o3_foresttype.RData")
sub_o3_leaftrait <- readRDS("./model/sub_o3_leaftrait.RData")
# nox
sub_nox_foresttype <- readRDS("./model/sub_nox_foresttype.RData")
sub_nox_leaftrait <- readRDS("./model/sub_nox_leaftrait.RData")
```

### draw leaf shape

```{r draw_leaf_trait}
trtname <- c("broadleaf", "coniferous")
nl <- c("NOx", "O3", "SO2", "PM")
leaft_nox <- extract_submeta(sub_nox_leaftrait$leaf_type_stulab, trtname, "NOx")
leaft_o3 <- extract_submeta(sub_o3_leaftrait$leaf_type_stulab, trtname, "O3")
leaft_so2 <- extract_submeta(sub_so2_leaftrait$leaf_type_caselab, trtname, "SO2")
leaft_pm <- extract_submeta(sub_pm_leaftrait$leaf_type_stulab, trtname, "PM")

leaft_summ <- bind_rows(leaft_nox$summarise, leaft_o3$summarise, 
                        leaft_so2$summarise, leaft_pm$summarise)

post_leaft <- bind_rows(leaft_nox$samples, leaft_o3$samples, 
                        leaft_so2$samples, leaft_pm$samples)

post_leaft <- post_leaft %>%
  mutate(pollutants = factor(pollutants, levels = nl))
leaft_summ <- leaft_summ %>%
  mutate(pollutants = factor(pollutants, levels = nl))
leaft_summ <- leaft_summ %>% 
  mutate(l95 = sprintf("%0.2f", lower95),
         u95 = sprintf("%0.2f", upper95),
         val = sprintf("%0.2f", value))
ant_lb <- "n,   mean,   95%CrI"

submeta_theme <- theme(panel.grid = element_blank(), 
                       panel.background = element_rect(fill = "white", color = "black"),
                       axis.title = element_text(size = 25), 
                       axis.text.x = element_text(size = 23), 
                       axis.text.y = element_text(size = 23), 
                       legend.position = "bottom", 
                       legend.text = element_text(size = 20))
y_axlb <- c("NOx" = expression(NO[x]), 
            "O3" = expression(O[3]),
            "SO2" = expression(SO[2]),
            "PM" = expression(PM))

fig_leaft <- ggplot(data = post_leaft, aes(x = value, y = pollutants, fill = types)) + 
  geom_text(data = leaft_summ, aes(label = glue("n={nobs}, {val}, [{l95}, {u95}]"), x = 0.7), hjust = "outward", vjust = 0.3, position = position_dodge(1), size = 6) + 
  stat_halfeye(.width = 0.95, size = 2, 
               position = position_dodge(1), 
               point_interval = mean_qi, scale = 1) + 
  geom_vline(xintercept = 0, linetype = "dashed", size = 1, color = "steelblue") + 
  geom_hline(yintercept = c(1.3, 2.3, 3.3), linetype = "twodash", color = "grey", size = 1) + 
  annotate(geom = "text", x = 0.7, y = 4.5, label = ant_lb, size = 6, hjust = "outward") + 
  scale_x_continuous(limits = c(-2.5, 3)) +
  labs(x = "Effect size (LnRR)", y = "") + 
  guides(fill = guide_legend(title = NULL)) + 
  scale_fill_manual(values = c("#00BFFF", "#FF3030")) + 
  scale_y_discrete(labels = y_axlb, expand = expansion(mult = c(0, 0.24))) + 
  submeta_theme

ggsave(filename = "./fig/fig_leaft.eps", plot = fig_leaft,
       width = 185, height = 250, units = "mm", limitsize = FALSE)
saveRDS(fig_leaft, "./fig/fig_leaft.RData")
```

```{r hyp_test_leaf_shape}
info_submeta(sub_nox_leaftrait$leaf_type_stulab)$hyp
info_submeta(sub_o3_leaftrait$leaf_type_stulab)$hyp
info_submeta(sub_so2_leaftrait$leaf_type_caselab)$hyp
info_submeta(sub_pm_leaftrait$leaf_type_stulab)$hyp
```

### draw forest type

```{r draw_leaf_trait}
trtname <- c("deciduous", "evergreen")
nl <- c("NOx", "O3", "SO2", "PM")
forestt_nox <- extract_submeta(sub_nox_foresttype$evergreen_forest_stulab, trtname, "NOx")
forestt_o3 <- extract_submeta(sub_o3_foresttype$evergreen_forest_stulab, trtname, "O3")
forestt_so2 <- extract_submeta(sub_so2_foresttype$evergreen_forest_caselab, trtname, "SO2")
forestt_pm <- extract_submeta(sub_pm_foresttype$evergreen_forest_stulab, trtname, "PM")

forestt_summ <- bind_rows(forestt_nox$summarise, forestt_o3$summarise, 
                        forestt_so2$summarise, forestt_pm$summarise)

post_forestt <- bind_rows(forestt_nox$samples, forestt_o3$samples, 
                        forestt_so2$samples, forestt_pm$samples)

post_forestt <- post_forestt %>%
  mutate(pollutants = factor(pollutants, levels = nl))
forestt_summ <- forestt_summ %>%
  mutate(pollutants = factor(pollutants, levels = nl))
forestt_summ <- forestt_summ %>% 
  mutate(l95 = sprintf("%0.2f", lower95),
         u95 = sprintf("%0.2f", upper95),
         val = sprintf("%0.2f", value))
ant_lb <- "n,   mean,   95%CrI"

submeta_theme <- theme(panel.grid = element_blank(), 
                       panel.background = element_rect(fill = "white", color = "black"),
                       axis.title = element_text(size = 25), 
                       axis.text.x = element_text(size = 23), 
                       axis.text.y = element_text(size = 23), 
                       legend.position = "bottom", 
                       legend.text = element_text(size = 20))
y_axlb <- c("NOx" = expression(NO[x]), 
            "O3" = expression(O[3]),
            "SO2" = expression(SO[2]),
            "PM" = expression(PM))

fig_forestt <- ggplot(data = post_forestt, aes(x = value, y = pollutants, fill = types)) + 
  geom_text(data = forestt_summ, aes(label = glue("n={nobs}, {val}, [{l95}, {u95}]"), x = 0.3), 
            hjust = "outward", vjust = 0.3, position = position_dodge(0.8), size = 6) + 
  stat_halfeye(.width = 0.95, size = 2, 
               position = position_dodge(0.85), 
               point_interval = mean_qi, scale = 1) + 
  geom_vline(xintercept = 0, linetype = "dashed", size = 1, color = "steelblue") + 
  geom_hline(yintercept = c(1.4, 2.44, 3.4), linetype = "twodash", color = "grey", size = 1) + 
  annotate(geom = "text", x = 0.3, y = 4.5, label = ant_lb, size = 6, hjust = "outward") + 
  scale_x_continuous(limits = c(-2, 2)) +
  labs(x = "Effect size (LnRR)", y = "") + 
  guides(fill = guide_legend(title = NULL)) + 
  scale_fill_manual(values = c("#FFC125", "#2E8B57")) + 
  scale_y_discrete(labels = y_axlb, expand = expansion(mult = c(0, 0.26))) + 
  submeta_theme 


ggsave(filename = "./fig/fig_forestt.eps", plot = fig_forestt,
       width = 185, height = 250, units = "mm", limitsize = FALSE)

saveRDS(fig_forestt, "./fig/fig_forestt.RData")
```

```{r hyp_test_forest}
info_submeta(sub_nox_foresttype$evergreen_forest_stulab)$hyp
info_submeta(sub_o3_foresttype$evergreen_forest_stulab)$hyp
info_submeta(sub_so2_foresttype$evergreen_forest_caselab)$hyp
info_submeta(sub_pm_foresttype$evergreen_forest_stulab)$hyp
```

### combine two figure together

```{r plot_trait}
fig_trat <- ggarrange(fig_leaft, fig_forestt,
                      ncol = 2,
                      font.label = list(size = 25, face = "bold"),
                      labels = letters[1:2])
ggsave(filename = "./fig/fig3.eps", plot = fig_trat,
       width = 400, height = 200, units = "mm", limitsize = FALSE)
saveRDS(fig_trat, "./fig/fig3.RData")

```



# Figure 4: Summary of the frequency of patterns in each case

## Prepare data

```{r prepare_data_for_pattern_analysis}
es_regdivlite <- es_regdiv %>% 
  dplyr::select(author, year, area, Journal, method, p_type1, stulab, stuid, caselab, 
         obid_l1, es_adj, var_adj, se_adj, `dominant species`, family, 
         leaf_type, evergreen_forest, habitus) %>%
  mutate(reduction = ifelse(es_adj > 0, "None", "Reduction"))

es_divwider <- es_regdivlite %>%
  dplyr::select(p_type1, family, reduction, obid_l1, es_adj, se_adj) %>%
  pivot_wider(names_from = family, values_from = family) %>% 
  pivot_wider(names_from = p_type1, values_from = p_type1) %>%
  rename(Others = None) %>%
  dplyr::select(-obid_l1, -es_adj, -se_adj) %>%
  relocate(PM, NOX, O3, SO2, .after = reduction) %>%
  dplyr::select(reduction, PM, NOX, O3, SO2, Podocarpaceae, 
         Cupressaceae, Ginkgoaceae, Sapindaceae,
         Platanaceae, Salicaceae, Betulaceae, Lauraceae,
         Fagaceae, Oleaceae, Moraceae, Fabaceae, Pinaceae, Others)
divna <- is.na(es_divwider)
es_divwider[divna] <- "None"
es_divwider <- es_divwider %>%
  mutate(reduction = ifelse(reduction == "Reduction", "ob", "None"))
sreduction <- es_divwider$reduction
es_divwider[!divna] <- "ob"
es_divwider$reduction <- sreduction
```


## Draw the figure

```{r draw_the_results_of_pattern_analysis}
setEPS(width = 10, height = 8)
postscript("./fig/fig4.eps")
zPatterns(es_divwider, label = "ob", axis.labels = c("Effect", "Pattern"),
          bar.ordered = c(TRUE, FALSE), bar.labels = TRUE, 
          cell.colors = c("#2E8B57", "white"), cell.labels = c("Observed","Unobserved"),
          bar.colors = c("ff9933", "ff9933"))
dev.off()
```

# Figure 5:  Meta-regression

## Functions for build regression models

```{r single_term_regression}
# This function builds a meta regression model based on the fixed and random effects of input
# popef: fixed effect
# grpef: random effect
# brmspara: parameters for brms function
# high memory demand for this function, better run in systems > 16GB
reg_single <- function(data, popef, grpef, brmspara){
  mod_formula <- t(outer(popef, grpef, FUN = paste_formual))
  mod_names <- t(outer(popef, grpef, FUN = paste, sep = "_"))
  mod_formula <- as.character(mod_formula)
  mod_names <- as.character(mod_names)
  print(paste("We have", length(mod_formula), "models.", sep = " "))
  brms_list <- vector(mode = "list", length = length(mod_formula))
  for(i in seq_along(mod_formula)){
    print(paste("Fitting model:", mod_formula[i], sep = " "))
    mod_i <- brm(formula = formula(mod_formula[i]), data = data,
                 cores = brmspara$cores, seed = brmspara$seed, iter = brmspara$iter,
                 control = list(max_treedepth = brmspara$max_treedepth,
                                adapt_delta = brmspara$adapt_delta))
    brms_list[[i]] <- mod_i
  }
  names(brms_list) <- mod_names
  return(brms_list)
}

# This function automatically extract regression information from a meta-regression model
info_regmodel <- function(brmsfit){
  model_f <- as.character(brmsfit$formula)[1]
  slope_name <- model_f %>%
    str_extract("\\~.*?\\+") %>%
    str_remove("\\~ ") %>%
    str_remove(" \\+")
  n_obs <- nrow(brmsfit$data)
  fix_mod <- fixef(brmsfit)[2, 1]
  if(fix_mod > 0){
    test_mod <- hypothesis(brmsfit, paste(slope_name, ">0", sep =""))
    test_mod_pval <- round(test_mod$hypothesis$Post.Prob, 2)
    test_reslabel <- paste("Pr(slope > 0) = ", test_mod_pval, sep = "")
  }else{
    test_mod <- hypothesis(brmsfit, paste(slope_name, "<0", sep = ""))
    test_mod_pval <- round(test_mod$hypothesis$Post.Prob, 2)
    test_reslabel <- paste("Pr(slope < 0) = ", test_mod_pval, sep = "")
  }
  nobs_label <- paste("N = ", n_obs, sep = "")
  model_r2 <- bayes_R2(brmsfit)
  r2_label <- paste("R2=", round(model_r2[, 1], 2), 
                    " [", round(model_r2[, 3], 2), ", ", 
                    round(model_r2[, 4], 2), "]", sep = "")
  model_summ <- paste(nobs_label, "\n", r2_label, "\n", test_reslabel, sep = "")
  return(model_summ)
}
# draw a scatter point for regression model
# brmsfit: brmsfit object
# theme: theme for plot
# xlab, ylab: labs for plot
# posx, posy: position for text label 
# fill: color for points
# limits_x, limits_y: scale limits
# modeltext: draw the information of regression model?
draw_regmodel <- function(brmsfit, theme, xlab, ylab, posx, posy, 
                          fill, limits_x = NULL, limits_y = NULL,
                          modeltext = TRUE){
  model_f <- as.character(brmsfit$formula)[1]
  slope_name <- model_f %>%
    str_extract("\\~.*?\\+") %>%
    str_remove("\\~ ") %>%
    str_remove(" \\+")
  model_data <- brmsfit$data
  n_obs <- nrow(model_data)
  colnames(model_data)[3] <- "mod"
  model_cond <- conditional_effects(brmsfit)
  smooth_x <- eval(parse(text = paste("model_cond", "$", slope_name, "$", slope_name, sep = "")))
  smooth_y <- eval(parse(text = paste("model_cond", "$", slope_name, "$", "estimate__", sep = "")))
  smooth_ymin <- eval(parse(text = paste("model_cond", "$", slope_name, "$", "lower__", sep = "")))
  smooth_ymax <- eval(parse(text = paste("model_cond", "$", slope_name, "$", "upper__", sep = "")))
  fix_mod <- fixef(brmsfit)[2, 1]
  if(fix_mod > 0){
    test_mod <- hypothesis(brmsfit, paste(slope_name, ">0", sep =""))
    test_mod_pval <- round(test_mod$hypothesis$Post.Prob, 2)
    test_reslabel <- paste("Pr(slope > 0) = ", test_mod_pval, sep = "")
  }else{
    test_mod <- hypothesis(brmsfit, paste(slope_name, "<0", sep = ""))
    test_mod_pval <- round(test_mod$hypothesis$Post.Prob, 2)
    test_reslabel <- paste("Pr(slope < 0) = ", test_mod_pval, sep = "")
  }
  nobs_label <- paste("N = ", n_obs, sep = "")
  model_r2 <- bayes_R2(brmsfit)
  r2_label <- paste("R2=", round(model_r2[, 1], 2), 
                    " [", round(model_r2[, 3], 2), ", ", 
                    round(model_r2[, 4], 2), "]", sep = "")
  model_summ <- ifelse(modeltext,
                       paste(nobs_label, "\n", r2_label, "\n", test_reslabel, sep = ""),
                       "")
  
  
  fig <- ggplot() + 
    geom_smooth(aes(x = smooth_x, y = smooth_y, ymin = smooth_ymin, ymax = smooth_ymax),
                    stat = "identity", size = 1.5, linetype = 1, alpha = 1, fill = "#D4D4D4")+
    geom_point(aes(x = mod, y = es_adj, size = se_adj), 
               data = model_data, shape = 21, fill = fill) + 
    geom_hline(yintercept = 0, lty = "dotted") + 
    annotate(geom = 'text', x = posx, y = posy, size = 6, label = model_summ) + 
    labs(x = xlab, y = ylab) +
    scale_y_continuous(limits = limits_y) + 
    scale_x_continuous(limits = limits_x) +
    theme
  return(fig)
}

```

## Build the regression models

### O3 regression models
```{r o3_regression}
o3_all <- es_regdata %>% filter(p_type1 == "O3")
popef <- c("distance", "ave_con", "rh", "wind", "temperature", "greencover")
grpef <- c("stulab","caselab")

brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 3000,
                 max_treedepth = 14, adapt_delta = 0.99)
reg_o3_allpoint <- reg_single(data = o3_all, popef = popef, grpef = grpef, brmspara = brmspara)

saveRDS(reg_o3_allpoint, "./model/reg_o3_allpoint.RData")
```

### NOx regression models
```{r nox_regression}
nox_all <- es_regdata %>% filter(p_type1 == "NOX")
popef <- c("distance", "ave_con", "rh","temperature", "greencover", "wind")
grpef <- c("stulab", "caselab")

brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 3000,
                 max_treedepth = 14, adapt_delta = 0.99)
reg_nox_allpoint <- reg_single(data = nox_all, popef = popef, grpef = grpef, brmspara = brmspara)

saveRDS(reg_nox_allpoint, "./model/reg_nox_allpoint.RData")
```

### SO2 regression models
```{r SO2_regression}
so2_all <- es_regdata %>% filter(p_type1 == "SO2")
brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 3000,
                 max_treedepth = 14, adapt_delta = 0.99)
popef <- c("distance", "ave_con","temperature", "greencover", "wind", "rh")
grpef <- c("caselab", "stulab")

reg_so2_allpoint <- reg_single(data = so2_all, popef = popef, grpef = grpef, brmspara = brmspara)
saveRDS(reg_so2_allpoint, "./model/reg_so2_allpoint.RData")
```

### PM regression models
```{r PM_regression}
pm_all <- es_regdata %>% filter(p_type1 == "PM")
popef <- c("ave_con", "greencover", "wind", "rh")
grpef <- c("caselab")

popef <- c("distance", "temperature")
grpef <- c("stulab")

brmspara <- list(cores = 8L, seed = 1234, prior = NULL, iter = 3000,
                 max_treedepth = 14, adapt_delta = 0.99)
reg_pm_allpoint <- reg_single(data = pm_all, popef = popef, grpef = grpef, brmspara = brmspara)
reg_pm_allpoint2 <- reg_single(data = pm_all, popef = popef, grpef = grpef, brmspara = brmspara)
saveRDS(reg_pm_allpoint, "./model/reg_pm_allpoint.RData")
```

## Draw the results of regression models

### NOx regression plot

```{r NOx regression plot}
reg_theme <- theme(panel.grid = element_blank(), 
                   panel.background = element_rect(fill = "white", color = "black"),
                   legend.position = 'none', 
                   axis.title = element_text(size = 20), 
                   axis.text.x = element_text(size = 15),
                   axis.text.y = element_text(size = 15))

reg_nox_allpoint <- readRDS("./model/reg_nox_allpoint.RData")
fig_nox_distance <- draw_regmodel(reg_nox_allpoint$distance_stulab,
                                  theme = reg_theme,
                                  xlab = "Distance (m)",
                                  ylab = "",
                                  posx = 0, posy = 0,
                                  fill = color_forest$nox_fill,
                                  modeltext = F)
  
fig_nox_conc <- draw_regmodel(reg_nox_allpoint$ave_con_stulab,
                              theme = reg_theme,
                              xlab = latex2exp::TeX("Concentration ($\\mu$g)"),
                              ylab = "",
                              posx = 0, posy = 0,
                              fill = color_forest$nox_fill,
                              modeltext = F)

fig_nox_green <- draw_regmodel(reg_nox_allpoint$greencover_caselab,
                               theme = reg_theme,
                               xlab = "Green area coverage (%)",
                               ylab = "",
                               posx = 0, posy = 0,
                               fill = color_forest$nox_fill,
                               modeltext = F)

fig_nox_airt <- draw_regmodel(reg_nox_allpoint$temperature_caselab, 
                              theme = reg_theme, 
                              xlab = "Air temeperature (°C)",
                              ylab = "",
                              posx = 0, posy = 0,
                              fill = color_forest$nox_fill,
                              modeltext = F)

fig_nox_rh <- draw_regmodel(reg_nox_allpoint$rh_stulab,
                            theme = reg_theme,
                            xlab = "Relative humidity (%)",
                            ylab = "",
                            posx = 0, posy = 0,
                            fill = color_forest$nox_fill,
                            modeltext = F,
                            limits_x = c(45, 90))

fig_nox_ws <- draw_regmodel(reg_nox_allpoint$wind_stulab,
                            theme = reg_theme,
                            xlab = "Wind speed (m/s)",
                            ylab = "",
                            posx = 0, posy = 0,
                            fill = color_forest$nox_fill,
                            modeltext = F)

fig_nox_list <- list(fig_nox_distance, fig_nox_conc, fig_nox_green,
                     fig_nox_airt, fig_nox_rh, fig_nox_ws)
fig_nox_all <- ggarrange(plotlist = fig_nox_list, 
                         labels = letters[1:6], 
                         ncol = 3, nrow =2, 
                         align = "v")

ggsave(file = "./fig/fig_nox_all.eps", 
       plot = fig_nox_all, 
       width = 300, height = 150, 
       units = "mm", limitsize = FALSE)
saveRDS(fig_nox_all,
        file = "./fig/fig_nox_all.RData")
```

### SO2 regression plot

```{r so2 regression plot}
reg_so2_allpoint <- readRDS("./model/reg_so2_allpoint.RData")

fig_so2_distance <- draw_regmodel(reg_so2_allpoint$distance_caselab,
                                  theme = reg_theme,
                                  xlab = "Distance (m)",
                                  ylab = "",
                                  posx = 0, posy = 0,
                                  fill = color_forest$so2_fill,
                                  modeltext = F)
  
fig_so2_conc <- draw_regmodel(reg_so2_allpoint$ave_con_caselab,
                              theme = reg_theme,
                              xlab = latex2exp::TeX("Concentration ($\\mu$g)"),
                              ylab = "",
                              posx = 0, posy = 0,
                              fill = color_forest$so2_fill,
                              modeltext = F)

fig_so2_green <- draw_regmodel(reg_so2_allpoint$greencover_caselab,
                               theme = reg_theme,
                               xlab = "Green area coverage (%)",
                               ylab = "",
                               posx = 0, posy = 0,
                               fill = color_forest$so2_fill,
                               modeltext = F)

fig_so2_airt <- draw_regmodel(reg_so2_allpoint$temperature_caselab, 
                              theme = reg_theme, 
                              xlab = "Air temeperature (°C)",
                              ylab = "",
                              posx = 0, posy = 0,
                              fill = color_forest$so2_fill,
                              modeltext = F)

fig_so2_rh <- draw_regmodel(reg_so2_allpoint$rh_stulab,
                            theme = reg_theme,
                            xlab = "Relative humidity (%)",
                            ylab = "",
                            posx = 0, posy = 0,
                            fill = color_forest$so2_fill,
                            limits_x = c(47, 80),
                            modeltext = F)

fig_so2_ws <- draw_regmodel(reg_so2_allpoint$wind_caselab,
                            theme = reg_theme,
                            xlab = "Wind speed (m/s)",
                            ylab = "",
                            posx = 0, posy = 0,
                            fill = color_forest$so2_fill,
                            modeltext = F)

fig_so2_list <- list(fig_so2_distance, fig_so2_conc, fig_so2_green,
                     fig_so2_airt, fig_so2_rh, fig_so2_ws)
fig_so2_all <- ggarrange(plotlist = fig_so2_list, 
                         labels = letters[13:18], 
                         ncol = 3, nrow = 2,
                         align = "v")

ggsave(file = "./fig/fig_so2_all.eps", 
       plot = fig_so2_all, 
       width = 300, height = 150, 
       units = "mm", limitsize = FALSE)
saveRDS(fig_so2_all,
        file = "./fig/fig_so2_all.RData")
```

### O3 regression plot

```{r o3 regression plot}
reg_o3_allpoint <- readRDS("./model/reg_o3_allpoint.RData")
fig_o3_distance <- draw_regmodel(reg_o3_allpoint$distance_caselab,
                                  theme = reg_theme,
                                  xlab = "Distance (m)",
                                  ylab = "",
                                  posx = 0, posy = 0,
                                  fill = color_forest$o3_fill,
                                  modeltext = F)
  
fig_o3_conc <- draw_regmodel(reg_o3_allpoint$ave_con_caselab,
                              theme = reg_theme,
                              xlab = latex2exp::TeX("Concentration ($\\mu$g)"),
                              ylab = "",
                              posx = 0, posy = 0,
                              fill = color_forest$o3_fill,
                              modeltext = F)

fig_o3_green <- draw_regmodel(reg_o3_allpoint$greencover_stulab,
                               theme = reg_theme,
                               xlab = "Green area coverage (%)",
                               ylab = "",
                               posx = 0, posy = 0,
                               fill = color_forest$o3_fill,
                               modeltext = F,
                               limits_x = c(0.05,0.85))

fig_o3_airt <- draw_regmodel(reg_o3_allpoint$temperature_stulab, 
                              theme = reg_theme, 
                              xlab = "Air temeperature (°C)",
                              ylab = "",
                              posx = 0, posy = 0,
                              fill = color_forest$o3_fill,
                              modeltext = F,
                              limits_x = c(8, 32))

fig_o3_rh <- draw_regmodel(reg_o3_allpoint$rh_caselab,
                            theme = reg_theme,
                            xlab = "Relative humidity (%)",
                            ylab = "",
                            posx = 0, posy = 0,
                            fill = color_forest$o3_fill,
                            modeltext = F,
                            limits_x = c(50, 85))

fig_o3_ws <- draw_regmodel(reg_o3_allpoint$wind_caselab,
                            theme = reg_theme,
                            xlab = "Wind speed (m/s)",
                            ylab = "",
                            posx = 0, posy = 0,
                            fill = color_forest$o3_fill,
                            modeltext = F)

fig_o3_list <- list(fig_o3_distance, fig_o3_conc, fig_o3_green,
                     fig_o3_airt, fig_o3_rh, fig_o3_ws)
fig_o3_all <- ggarrange(plotlist = fig_o3_list, 
                        labels = letters[7:12], 
                        ncol = 3, nrow = 2,  
                        align = "v")

ggsave(file = "./fig/fig_o3_all.eps", 
       plot = fig_o3_all, 
       width = 300, height = 150, 
       units = "mm", limitsize = FALSE)
```

### PM regression plot

```{r pm regression plot}
reg_pm_allpoint <- readRDS("./model/reg_pm_allpoint.RData")
fig_pm_distance <- draw_regmodel(reg_pm_allpoint$distance_stulab,
                                  theme = reg_theme,
                                  xlab = "Distance (m)",
                                  ylab = "",
                                  posx = 0, posy = 0,
                                  fill = color_forest$pm_fill,
                                  modeltext = F)
  
fig_pm_conc <- draw_regmodel(reg_pm_allpoint$ave_con_caselab,
                              theme = reg_theme,
                              xlab = latex2exp::TeX("Concentration ($\\mu$g)"),
                              ylab = "",
                              posx = 0, posy = 0,
                              fill = color_forest$pm_fill,
                              modeltext = F)

fig_pm_green <- draw_regmodel(reg_pm_allpoint$greencover_caselab,
                               theme = reg_theme,
                               xlab = "Green area coverage (%)",
                               ylab = "",
                               posx = 0, posy = 0,
                               fill = color_forest$pm_fill,
                               modeltext = F)

fig_pm_airt <- draw_regmodel(reg_pm_allpoint$temperature_caselab, 
                              theme = reg_theme, 
                              xlab = "Air temeperature (°C)",
                              ylab = "",
                              posx = 0, posy = 0,
                              fill = color_forest$pm_fill,
                              modeltext = F)

fig_pm_rh <- draw_regmodel(reg_pm_allpoint$rh_caselab,
                            theme = reg_theme,
                            xlab = "Relative humidity (%)",
                            ylab = "",
                            posx = 0, posy = 0,
                            fill = color_forest$pm_fill,
                            modeltext = F,
                            limits_x = c(42, 95))

fig_pm_ws <- draw_regmodel(reg_pm_allpoint$wind_caselab,
                            theme = reg_theme,
                            xlab = "Wind speed (m/s)",
                            ylab = "",
                            posx = 0, posy = 0,
                            fill = color_forest$pm_fill,
                            modeltext = F)

fig_pm_list <- list(fig_pm_distance, fig_pm_conc, fig_pm_green,
                     fig_pm_airt, fig_pm_rh, fig_pm_ws)
fig_pm_all <- ggarrange(plotlist = fig_pm_list, 
                        labels = letters[19:24], 
                        ncol = 3, nrow = 2,
                        align = "v")

ggsave(file = "./fig/fig_pm_all.eps", 
       plot = fig_pm_all, 
       width = 300, height = 150, 
       units = "mm", limitsize = FALSE)
saveRDS(fig_pm_all,
        file = "./fig/fig_pm_all.RData")
```

### All regression plot

```{r draw_all_regression}
fig_reg_list <- c(fig_nox_list, fig_o3_list, fig_so2_list, fig_pm_list)

fig_reg_all <- ggarrange(plotlist = fig_reg_list, 
                        labels = letters[1:24], 
                        ncol = 3, nrow = 8,  
                        align = "v")

ggsave(file = "./fig/fig_reg_all.eps", 
       plot = fig_reg_all, 
       width = 300, height = 700, 
       units = "mm", limitsize = FALSE)
saveRDS(fig_reg_all,
        file = "./fig/fig_reg_all.RData")
```

# Figure 6 The perspectives of urban environmental managers on air phytoremediation in Shenzhen

## Prepare data

```{r prepare_data}
# questionnaire data
sz_quesd <- read.csv(file = "./data/sz_questionnaire.csv",
                     stringsAsFactors = FALSE)
colnames(sz_quesd)[7] <- "PM"

ques_res <- read.csv(file = "./data/questionnaire_perceptions.csv")
ques_res <- ques_res %>%
  mutate(op = factor(op, levels = c(c("Worsen air pollution", "Non-influence", 
                                      "Mitigate air pollution"))))


sz_pattern <- sz_quesd %>% 
  dplyr::select(PM, NOX, SO2, O3) %>%
  count(PM, NOX, SO2,O3) %>%
  arrange(desc(n)) %>%
  mutate(percentage = round(n/nrow(sz_quesd), 4)*100)
sz_patternl <- sz_pattern %>% 
  mutate(patternid = factor(c(1:nrow(sz_pattern)), 
                            levels = rev(1:nrow(sz_pattern)))) %>%
  pivot_longer(cols = c("PM", "NOX", "SO2", "O3"),
               names_to = "Pollutants",
               values_to = "Response") %>%
  mutate(Pollutants = factor(Pollutants, levels = c("PM", "NOX", "SO2", "O3")))

theme_pattern <- theme(panel.grid = element_line(linetype = "dashed", 
                                                 color = "black"),
                       panel.background = element_rect(fill = NULL, 
                                                       colour ="black"))
sz_patternl_sel <- sz_patternl %>% 
  filter(percentage > quantile(percentage, 0.5))
nid <- sz_patternl_sel$patternid %>%
  unique() %>%
  length()
```

## Draw the figure

```{r fig6_draw}
# pattern figure
library(cowplot)
fig_quespat <- sz_patternl_sel %>%
  ggplot(aes(x = Pollutants, y = patternid, fill = Response))+
  geom_tile(alpha = 1)+
  geom_vline(xintercept = c(1.5, 2.5, 3.5), linetype = "dashed") +
  geom_vline(xintercept = 4.5, color = "black") + 
  geom_hline(yintercept = c(2:nid-1) + 0.5, 
             linetype = "dashed")+
  scale_fill_manual(values = c("#ED876B", "#F7DC9C", "#77D9A0")) + 
  scale_y_discrete(expand = expansion(mult = c(0, 0)),
                   breaks = c("1", "5", "10", "15", "20")) +
  scale_x_discrete(expand = expansion(mult = c(0, 0)),
                   labels = c(expression(PM), expression(NO[x]),  expression(SO[2]), expression(O[3]))) + 
  ggtitle("b")+
  theme(panel.background = element_rect(fill = "white", color = "black"),
        axis.line.y = element_line(colour ="black"),
        legend.position = "none",
        axis.title = element_text(face = "bold", colour = "black", size = 30),
        axis.text = element_text(face = "bold", color = "black", size = 25))

sz_pattern_sel <- sz_pattern %>%
  filter(percentage > quantile(percentage, 0.5)) %>%
  mutate(perf = factor(percentage)) %>%
  mutate(perf = factor(perf, levels = rev(levels(perf))))
sz_pattern_sel <- sz_pattern_sel %>% 
  mutate(patternid = factor(c(1:nrow(sz_pattern_sel)), 
                              levels = rev(1:nrow(sz_pattern_sel))))

# marginal frequency for patterns
pal_for_bar <- c( "#FF4040", "#FF7256", "#FFAEB9", 
                  "#EED5D2", "#6495ED", "#B0E0E6", 
                  "#97FFFF", "#D1EEEE", "#CCCCCC", 
                  "#737373", "#383838")

fig_paternbar <- ggplot(sz_pattern_sel, aes(y = patternid, x= percentage)) + 
  geom_bar(stat = "identity", aes(fill = perf)) + 
  scale_fill_manual(values = pal_for_bar) + 
  theme_half_open() +
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text = element_blank())

fig_ques <- ggplot(data = ques_res) + 
  geom_bar(aes(x = prop, y = p_type, fill = op), stat = "identity", 
           width = 0.5) + 
  geom_text(aes(x = textpos, y = p_type, label = prop), color = "black", size = 10) + 
  labs(x = "Proportion (%)", y = "")+
  scale_fill_manual(values =  c("#ED876B", "#F7DC9C", "#77D9A0")) + 
  scale_y_discrete(labels = c(expression(NO[x]), expression(O[3]), expression(PM[2.5]), expression(SO[2]))) + 
  ggtitle("a") + 
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        panel.background = element_rect(color = "black", fill = "white"),
        axis.text = element_text(size = 25, color = "black"),
        axis.title = element_text(size = 30, color = "black"),
        axis.ticks.length = unit(-0.1, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size = 25, color = "black"))


library(patchwork)
# using patchwork to define grid

fig_pattern <- fig_ques/(fig_quespat + fig_paternbar + plot_layout(width = c(2, 1)))

ggsave("./fig/fig_pattern.eps", plot = fig_pattern,
       width = 300, height = 300, units = "mm", limitsize = FALSE)
```

# Figure 8 The international distribution of case studies.

## Data prepared

```{r fig8_data}
count_ptype1 <- es_regdata %>% count(p_type1)
count_cty <- es_regdata %>% count(country)
count_year <- table(es_regdata %>% count(stulab, year) %>% dplyr::select(year))
count_year <- count_year %>%
  data.frame() %>% 
  rename(year = Var1, n = Freq) %>%
  arrange(year) %>%
  mutate(yearf = factor(year, levels = year),
         grp = "A")
```

## draw the figure

### Types of pollutants

```{r draw_types_of_pollutants}
library(ggforce)

fig_ptype1 <- ggplot(data = count_ptype1) + 
  geom_arc_bar(aes(x0 = 0 , y0 = 0, r0 = 0, r = 1, 
                   amount = n, fill = p_type1, explode = c(0.05, 0.05, 0.05, 0.05)),
               stat = "pie", color = "#4F4F4F", size = 1) + 
  scale_fill_manual(values = c("#ffa9e0", "#9fb8fb",
                               "#ffe3a7", "#d7d7d7")) + 
  theme_no_axes() + 
  theme(legend.position = "none", 
        legend.title = element_blank(),
        legend.text = element_text(size = 15),
        panel.border = element_blank())

ggsave("./fig/fig_ptype1.eps",
       width = 100, height = 100, units = "mm",
       limitsize = FALSE)

saveRDS(fig_ptype1, "./fig/fig_ptype1.RData")

```

### country

```{r draw_country}

count_cty <- count_cty %>%
  arrange(desc(n))
lb <- c(count_cty$country[1:9], rep("Other countries", 8))
count_cty2 <- count_cty %>%
  mutate(ctylb = lb) %>% 
  group_by(ctylb) %>%
  summarise(n2 = sum(n)) %>%
  arrange(desc(n2)) %>%
  mutate(ctylbf  = factor(ctylb, levels = ctylb)) %>%
  mutate(ctylbf = relevel(ctylbf, ref = "Other countries"))

count_cty3 <- count_cty[10:17, ] %>%
  mutate(ctylbf = factor(country, levels = country))

fill_manual <- c("#F7F7F7", "#FF4040", "#FF7256", "#FFAEB9", 
                  "#EED5D2", "#6495ED", "#B0E0E6", 
                  "#97FFFF", "#D1EEEE", "#CCCCCC")

fig_country <- ggplot(data = count_cty2) + 
  geom_arc_bar(aes(x0 = 0 , y0 = 0, r0 = 0, r = 1, 
                   amount = n2, fill = ctylbf),
               stat = "pie", color = "#4F4F4F", size = 1) + 
  theme_no_axes() + 
  theme(legend.position = "bottom", 
        legend.title = element_blank(),
        legend.text = element_text(size = 15),
        panel.border = element_blank()) + 
  scale_fill_manual(values = fill_manual)

fig_othercountry <- ggplot(data = count_cty3) + 
  geom_arc_bar(aes(x0 = 0 , y0 = 0, r0 = 0, r = 1, 
                   amount = n, fill = ctylbf),
               stat = "pie", color = "#4F4F4F", size = 1) + 
  theme_no_axes() + 
  theme(legend.position = "top", 
        legend.title = element_blank(),
        legend.text = element_text(size = 15),
        panel.border = element_blank()) + 
  scale_fill_manual(values = fill_manual[2:9])

ggsave("./fig/fig_country.eps", fig_country, 
       width = 300, height = 300, units = "mm",
       limitsize = FALSE)

ggsave("./fig/fig_othercountry.eps", fig_othercountry, 
       width = 200, height = 200, units = "mm",
       limitsize = FALSE)

```

### Publication year

```{r draw_publication_year}
fig_year <- ggplot(data = count_year, aes(x = yearf, y = n, group = grp)) + 
  geom_bar(stat = "identity", fill = "darkblue") + 
  geom_point(size = 4, colour = "#FF7F00") + 
  geom_smooth(method = "lm", se = F, color = "darkred", 
              linetype = 4, size = 2) + 
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30)) + 
  reg_theme + 
  theme(legend.title = element_text(size = 20, colour = "black", face = "bold"),
        legend.position = "bottom",
        axis.text.x = element_text(colour = "black", face = "bold", size = 20, angle = 45, hjust = 1),
        axis.text.y = element_text(colour = "black", face = "bold", size = 20),
        axis.title = element_text(colour = "black", face = "bold", size = 20),
        legend.text = element_text(colour = "black", face = "bold", size = 15),
        legend.key.width = unit(5.5, "cm"))+ 
  labs(x = "", y = "Number of researches")

ggsave(filename = "./fig/fig_year.eps",fig_year,
       width = 300, height = 300, 
       units = "mm",limitsize = FALSE)
```

### Combine figure

```{r combine_year_and_country}
fig_yearcty <- ((fig_country+fig_othercountry + plot_layout(widths = c(1, 1)))|fig_year) + 
  plot_layout(widths = c(2, 1))

ggsave(filename = "./fig/fig_yearcty.eps",fig_yearcty,
       width = 450, height = 190,
       units = "mm", limitsize = FALSE)
```




